---
title: "Luxury Handbag Auction Analysis"
output: pdf_document
date: "2022-10-20"
---

# 0.Load data and libraries
```{r}
library(readxl)
library(magrittr)
library(tidyr)
library(stringr)
library(dbplyr)
```

```{r}
data <- read_excel('auction_dataset_raw data.xlsx')
head(data)
```

# 1. Business Understanding
**Luxury Handbag Auction Analysis**

**Business Problem**:
Taking inspiration from the luxury value perception model proposed by Weidman et al., this project explores the individual, functional, social and financial value of a handbag based on the following attributes – uniqueness, quality, prestige, vintage, and sold price. This model can thus be used to understand the market better according to the relevant dimensions of luxury perception.
***More importantly, in this project, I want to find out that what are some key indicators that determine the auction price.*** 

# 2. Data Processing
**Brand**
```{r}
#Brand
#unique(data$brand)
data$brand[grepl("Hermès", data$brand)] <- 'Hermès'
data$brand[grepl("Louis Vuitton", data$brand) | 
             grepl("LOUIS VUITTON", data$brand)] <- 'Louis Vuitton'
data$brand[grepl("Chanel", data$brand)] <- 'Chanel'
data$brand[grepl("Dior", data$brand)] <- 'Dior'
data$brand[grepl("Goyard", data$brand)] <- 'Goyard'
data$brand[grepl("Gucci", data$brand)] <- 'Gucci'
data$brand[grepl("Tiffany & Co.", data$brand)] <- 'Tiffany & Co.'
data$brand[grepl("FENDI", data$brand) |
             grepl("Fendi", data$brand)] <- 'Fendi'
data$brand[grepl("Gianni Versace", data$brand)] <- 'Gianni Versace'
data$brand[grepl("Bottega Veneta", data$brand)] <- 'Bottega Veneta'
data$brand[grepl("Bvlgari", data$brand)] <- 'Bvlgari'
data$brand[grepl("Alexander McQueen", data$brand)] <- 'Alexander McQueen'
data$brand[grepl("Etoupe Doblis", data$brand)] <- 'Etoupe Doblis'
unique(data$brand)
```
**Bag Characteristics**
1. Find leather type (Crocodile/Alligator/Ostrich/Others)
2. Find product year (Before 2002 or After 2002)
3. Find style (Birkin/Kelly/Constance/Roulis/Others)
4. Find color type (5- Others / 4 - Silver/Gold/Gris / 3 - Red/Rose/Organe/Pin / 2 - Blue / 1 - Black/White)

```{r}
#Leather
data$quality_4 <- ifelse(grepl("Crocodile", data$bag), 1, 0)
data$quality_3 <- ifelse(grepl("Alligator", data$bag), 1, 0)
data$quality_2 <- ifelse(grepl("Ostrich", data$bag), 1, 0)
```

If the bag is produced before 2002, defined as vintage
```{r}
#Year
data$production_year <- sub(".*?(\\d{4})$", "\\1", data$bag)
#data$production_year <- gsub("^, ", "", production_year)
data$production_year <- as.numeric(ifelse(grepl("\\D", data$production_year), 'no production year', data$production_year))
data$production_year[is.na(data$production_year)] <- 'no production year'
data$vintage <- ifelse((data$production_year >= 2002), 1, 0)
```

For bag without a production year, randomly fulfill (0,1) for vintage, following the true percentage of (0,1)
```{r}
#Year
table(data$vintage) #100:745
prop <- table(data$vintage, useNA = "no") / sum(!is.na(data$vintage))
data$vintage[is.na(data$vintage)] <- sample(c(0, 1), 
                                             size = sum(is.na(data$vintage)), 
                                              replace = TRUE, 
                                              prob = prop)
```


```{r}
#Style
data$prestige_5 <- ifelse(grepl("Birkin", data$bag), 1, 0)
data$prestige_4 <- ifelse(grepl("Kelly", data$bag), 1, 0)
data$prestige_3 <- ifelse(grepl("Constance", data$bag), 1, 0)
data$prestige_2 <- ifelse(grepl("Roulis", data$bag), 1, 0)

#Color
data$unique_4 <- ifelse(grepl("Sliver", data$bag) | grepl("Gold", data$bag) 
                        | grepl("Gris", data$bag), 1, 0)
data$unique_3 <- ifelse(grepl("Red", data$bag) | grepl("Rose", data$bag) 
                        | grepl("Orange", data$bag) | grepl("Pink", data$bag), 1, 0)
data$unique_2 <- ifelse(grepl("Blue", data$bag), 1, 0)
data$unique_1 <- ifelse(grepl("Black", data$bag) | grepl("White", data$bag), 1, 0)

```

**Price**
Estimate Price
1. Calculate mean estimate price
2. Convert currency to USD
```{r}
data$estimate <- gsub(",", "", data$estimate)  # Remove commas
data$estimate <- gsub("USD", "", data$estimate)  # Remove Currency
data$estimate <- gsub("HKD", "", data$estimate)  # Remove Currency
data$estimate <- gsub("CHF", "", data$estimate)  # Remove Currency
data$estimate <- gsub("GBP", "", data$estimate)  # Remove Currency
data$estimate <- gsub("EUR", "", data$estimate)  # Remove Currency
split_values <- strsplit(data$estimate, " - ")  # Split by " - "

data$estimate_low  <- as.numeric(sapply(split_values, "[", 1))  # Get first element
data$estimate_high <- as.numeric(sapply(split_values, "[", 2))  # Get second element
data$estimate_average <- rowMeans(data[,c('estimate_low','estimate_high')])
```

```{r}
#unique(data$Location)

conversion_rate <- c("New York" = 1, "Hong Kong" = 0.13, 'Geneva' = 0.9, 
                     'London' = 0.8, 'Milan' = 0.92, 'Paris ' = 0.92)

# Apply conversion rate to create new column
data$estimate_average_converted <- data$estimate_average * conversion_rate[data$Location]
```

```{r}
data$`sold price` <- gsub(",", "", data$`sold price`)  # Remove commas
data$`sold price` <- gsub("USD", "", data$`sold price`)  # Remove Currency
data$`sold price` <- gsub("HKD", "", data$`sold price`)  # Remove Currency
data$`sold price` <- gsub("CHF", "", data$`sold price`)  # Remove Currency
data$`sold price` <- gsub("GBP", "", data$`sold price`)  # Remove Currency
data$`sold price` <- gsub("EUR", "", data$`sold price`)  # Remove Currency
```

```{r}
data$`sold price`[is.na(data$`sold price`)] <- 0
data$`sold price` <- as.numeric(data$`sold price`)
data$sold_price_converted <- data$`sold price` * conversion_rate[data$Location]
```

```{r}
# Apply conversion rate to create new column
data$sold_price_converted <- data$`sold price` * conversion_rate[data$Location]
```

Brand: This variable represents the brand of the bags. The brands considered in this dataset include Hermès, Goyard, Chanel, Louis Vuitton, Alexander McQueen, Bvlgari, Dior, Gucci, Bottega Veneta, Tiffany & Co., Fendi, Gianni Versace, and Etoupe Doblis.

Location: This variable denotes the geographical location where the auction was held.

Auction year: This variable represents the year in which the auction took place.

quality_4: This binary variable indicates whether the bag is made from crocodile leather (1) or not (0).

quality_3: This binary variable signifies whether the bag is made from alligator leather (1) or not (0).

quality_2: This binary variable shows whether the bag is made from ostrich leather (1) or not (0).

vintage: This binary variable indicates whether the bag was manufactured before the year 2002 (1) or not (0).

prestige_5: This binary variable indicates whether the bag is a Birkin model (1) or not (0).

prestige_4: This binary variable signifies whether the bag is a Kelly model (1) or not (0).

prestige_3: This binary variable shows whether the bag is a Constance model (1) or not (0).

prestige_2: This binary variable indicates whether the bag is a Roulis model (1) or not (0).


unique_4: This variable denotes whether the bag's color is within the silver/gold/gris spectrum.

unique_3: This variable indicates whether the bag's color falls within the red/rose/orange/pink spectrum.

unique_2: This variable shows whether the bag's color is blue.

unique_1: This variable indicates whether the bag's color is black.

estimate_average_converted: This variable represents the midpoint of the estimated selling price range, in USD.

sold_price_converted: This variable denotes the actual price at which the bag was sold, in USD.

**Dataset For Modeling**

```{r}
clean_dataset <- data[,c('brand',
'Location',
'Auction year',
'quality_4',
'quality_3',
'quality_2',
'vintage',
'prestige_5',
'prestige_4',
'prestige_3',
'prestige_2',
'unique_4',
'unique_3',
'unique_2',
'unique_1',
'estimate_average_converted',
'sold_price_converted')]

write.csv(clean_dataset, 'clean_auction_dataset.csv')
```

**Dataset For Visualization**

```{r}
clean_dataset_visual <- data[,c('brand',
'Location',
'Auction year',
'production_year',
'estimate',
'quality_4',
'quality_3',
'quality_2',
'vintage',
'prestige_5',
'prestige_4',
'prestige_3',
'prestige_2',
'unique_4',
'unique_3',
'unique_2',
'unique_1',
'estimate_average_converted',
'sold_price_converted')]

write.csv(clean_dataset_visual, 'clean_auction_dataset_visualization.csv')
```
